---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LoveER

<!-- badges: start -->
<!-- badges: end -->

LoveER performs prediction of $Y$, estimation and inference of $\beta$ with 
statistical guarantees under the structured latent factor regression model 
$X = A\ Z+E$ and $Y = Z^\top \beta + \varepsilon.$

## Installation

<!-- the released version of LoveER from [CRAN](https://CRAN.R-project.org) with: -->
<!-- ``` r -->
<!-- install.packages("LoveER") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("bingx1990/LoveER")
```

It requires to pre-install the [LOVE](https://github.com/bingx1990/LOVE) package 
with 

``` r
devtools::install_github("bingx1990/LOVE")
```

## Example

This is a basic example which shows you how to use the ER package. We start by 
generating a synthetic data set. 

```{r data generating}
p <- 6
n <- 50
K <- 2
A <- rbind(c(1, 0), c(-1, 0), c(0, 1), c(0, 1), c(1/3, 2/3), c(1/2, -1/2))
Z <- matrix(rnorm(n * K, sd = 2), n, K)
E <- matrix(rnorm(n * p), n, p)
X <- Z %*% t(A) + E

eps <- rnorm(n)
beta <- c(1, -0.5)
Y <- Z %*% beta + eps
```

The following code calls the LOVE function to perform overlapping clustering of 
the columns of the $\mathbf{X}$ matrix. It should be noted that 
`pure_homo = TRUE` 
is required for downstream prediction of $Y$ and inference of $\beta$. 

```{r example-LOVE}
library(LOVE)
library(LoveER)
# overlapping clustering
res_LOVE <- LOVE(X, pure_homo = TRUE, delta = seq(0.1, 1.1 ,0.1))
```

To predict $Y$, estimate the coefficient $\beta$ and provide confidence
intervals of $\beta$, the following code provides an example.

```{r example-ER}
# use the output of LOVE to perform prediction and inference.
res_ER <- ER(Y, X, res_LOVE, CI = TRUE)
res_ER <- ER(Y, X, res_LOVE, beta_est = "Dantzig", CI = FALSE)
```


