---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LoveER

<!-- badges: start -->
<!-- badges: end -->

LoveER provides algorithms with statistical guarantees to 

* perform overlapping clustering of features under a structured latent factor model;
* perform prediction, estimation and inference under a structured latent factor 
  regression model.

## Installation

You can install the released version of LoveER from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("LoveER")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bingx1990/LoveER")
```
## Example

This is a basic example which shows you how to use two main functions of LoveER: 
LOVE and ER. We start by generating a synthetic data set. 

```{r data generating}
p <- 6
n <- 50
K <- 2
A <- rbind(c(1, 0), c(-1, 0), c(0, 1), c(0, 1), c(1/3, 2/3), c(1/2, -1/2))
Z <- matrix(rnorm(n * K, sd = 2), n, K)
E <- matrix(rnorm(n * p), n, p)
X <- Z %*% t(A) + E

eps <- rnorm(n)
beta <- c(1, -0.5)
Y <- Z %*% beta + eps
```

The following code calls the LOVE function to perform overlapping clustering of 
the columns of the \strong{X} matrix.

```{r example-LOVE}
library(LoveER)
# basic example code
res_LOVE <- LOVE(X)
```

To predict \eqn{Y}, estimate the coefficient \eqn{\beta} and provide confidence
intervals of \eqn{\beta}, the following code provides an example.

```{r example-ER}
res_ER <- ER(Y, X, res_LOVE, CI = TRUE)
```


